C/O in Protoplanetary Disks: The Effect of Radial Drift and Viscous Accretion

### 2015-07-16 tex/draft/ms.tex
update

\begin{figure*}[tb]
\centering
\includegraphics[width=\textwidth]{../../figs/desorption_distance_passive_active_colorbar_test.pdf}
%\vspace{-0.5in}
\caption{Desorption distance as a function of a particle's initial location in the disk, for a range of particle sizes, and for both a passive disk (left panels) and an active disk (right panels). The desorption distance is calculated for particles composed of H$_2$O (top panels), CO$_2$ (middle panels) and CO (bottom panels). The particle size increases from $10^{-3}$ cm to $10^8$ cm as indicated by the color bar. For the range of particle sizes that fully desorb during $t_{\rm d}=3$ Myr, the desorption distance is the same regardless of the particles' initial location.} 
\label{fig:snowlines}
\end{figure*}

\begin{figure*}[t!]
\centering
\includegraphics[width=0.7\textwidth]{../../figs/desorption_distance_actual_vs_estimated_passive_active.pdf}
%\vspace{-0.5in}
\caption{Desorption distance estimated from analytic calculations (see text) as a function of the desorption distance calculated numerically, for the range of particle sizes that desorb at a fixed distance regardless of their initial location (see Figure \ref{fig:snowlines} and text). The estimate is performed for a passive disk (left panels) and an active disk (right panels).  The particles are composed of H$_2$O (top panels), CO$_2$ (middle panels) and CO (bottom panels). The analytic approximation is in good agreement with the numerical result for most cases.}
\label{fig:an_vs_actual}
\end{figure*}

>>>>

\begin{figure*}[tb]
\centering
\includegraphics[width=0.7\textwidth]{../../figs/desorption_distance_passive_active_colorbar_test.pdf}
%\vspace{-0.5in}
\caption{Desorption distance as a function of a particle's initial location in the disk, for a range of particle sizes, and for both a passive disk (left panels) and an active disk (right panels). The desorption distance is calculated for particles composed of H$_2$O (top panels), CO$_2$ (middle panels) and CO (bottom panels). The particle size increases from $10^{-3}$ cm to $10^8$ cm as indicated by the color bar. For the range of particle sizes that fully desorb during $t_{\rm d}=3$ Myr, the desorption distance is the same regardless of the particles' initial location.} 
\label{fig:snowlines}
\end{figure*}

\begin{figure*}[t!]
\centering
\includegraphics[width=0.7\textwidth]{../../figs/desorption_distance_actual_vs_estimated_passive_active_new.pdf}
%\vspace{-0.5in}
\caption{Desorption distance estimated from analytic calculations (see text) as a function of the desorption distance calculated numerically, for the range of particle sizes that desorb at a fixed distance regardless of their initial location (see Figure \ref{fig:snowlines} and text). The estimate is performed for a passive disk (left panels) and an active disk (right panels).  The particles are composed of H$_2$O (top panels), CO$_2$ (middle panels) and CO (bottom panels). The analytic approximation is in good agreement with the numerical result for most cases.}
\label{fig:an_vs_actual}
\end{figure*}
